Time Series

### 2023-11-13 Preparation/effective_obs.qmd
add in some Heike-suggested diagnostics

-

>>>>

## Leaving out the last X%

df <- dplyr::filter(wce, !is.na(sig))

df[1:1500,]
aamodel <- auto.arima(y = df$sig[1:1500], xreg = df$x[1:1500], stepwise = FALSE, parallel = T)
summary(aamodel)

pred <- predict(aamodel, n.ahead = 500, newxreg = df$x[1501:2000]) %>%
  as.data.frame() %>%
  mutate(x = df$x[1501:2000], ypred = pred, ylow = ypred - 2*se, yhigh = ypred + 2*se)

ggplot(df, aes(x = x, y = sig)) + geom_line() + 
  geom_line(data = pred, aes(x = x, y = ypred), color = "red") + 
  geom_ribbon(data = pred, aes(x = x, y = ypred, ymin = ylow, ymax = yhigh), fill = "red", alpha = .2)
```
